Commit Rater

### 2015-08-25 presentations/paper/methodology.tex
Add \labels to all \sections
Fill in all times now that they're timed
Remove comma separators from numbers

\section{Methodology}
% The methodology section must give a very clear account of what sort of
% procedure was executed. Here are some detailed criteria:

@@

\begin{description}
    \item[101worker]\footnote{\url{https://github.com/101companies/101worker}}: A relatively small repository of barely over $2,000$ commits, done by the Software Languages Team of the University of Koblenz-Landau. Most of the commits in this repository do not adhere to the commit guidelines.
    \item[mozilla/openbadges-badgekit]\footnote{\url{https://github.com/mozilla/openbadges-badgekit/}}: % TODO why?
    \item[perl]\footnote{\url{https://github.com/Perl/perl5}}: The interpreter for Perl 5, a large repository of over $60,000$ commits, partially adhering the commit guidelines.
    \item[Linux Kernel]\footnote{\url{https://github.com/torvalds/linux}}: A massive repository of over half a million commits. Used for stress-testing our implementation and finding reasonable constraints on the amount of commits analyzed. Most commit messages adhere to the commit guidelines, for the sake of managing such a large volume of them.
\end{description}

@@

\begin{table}[t]
    \begin{tabularx}{\textwidth}{@{}|Y|Y|@{}}\hline
        \textbf{Repository} & \textbf{Time to Rate} \\\hline
        101worker & 10 seconds \\\hline
        BadgeKit & 4 seconds \\\hline
        perl & ? \\\hline
        Linux Kernel & ?\\\hline
    \end{tabularx}
    \caption{Time taken to clone repositories and rate their commits}
    \label{tab:time}
\end{table}

@@

However, to keep the prototype website usable for multiple users at once, we decided to limit the number of commits analyzed to the latest $10,000$ commits. However, this practical limit may be increased by allowing more worker processes to rate repositories at once, reducing the chance of the entire commit rater being blocked for a long time by large repositories.

>>>>

\section{Methodology}
\label{sec:methodology}
% The methodology section must give a very clear account of what sort of
% procedure was executed. Here are some detailed criteria:

@@

\begin{description}
    \item[101worker]\footnote{\url{https://github.com/101companies/101worker}}: A relatively small repository of barely over $2000$ commits, done by the Software Languages Team of the University of Koblenz-Landau. Most of the commits in this repository do not adhere to the commit guidelines.
    \item[mozilla/openbadges-badgekit]\footnote{\url{https://github.com/mozilla/openbadges-badgekit/}}: % TODO why?
    \item[perl]\footnote{\url{https://github.com/Perl/perl5}}: The interpreter for Perl 5, a large repository of over $60000$ commits, partially adhering the commit guidelines.
    \item[Linux Kernel]\footnote{\url{https://github.com/torvalds/linux}}: A massive repository of over half a million commits. Used for stress-testing our implementation and finding reasonable constraints on the amount of commits analyzed. Most commit messages adhere to the commit guidelines, for the sake of managing such a large volume of them.
\end{description}

@@

\begin{table}[t]
    \begin{tabularx}{\textwidth}{@{}|Y|Y|@{}}\hline
        \textbf{Repository} & \textbf{Time to Rate} \\\hline
        101worker & 10 seconds \\\hline
        BadgeKit & 4 seconds \\\hline
        perl & 3 minutes \\\hline
        Linux Kernel & 16 minutes\\\hline
    \end{tabularx}
    \caption{Time taken to clone repositories and rate their commits}
    \label{tab:time}
\end{table}

@@

However, to keep the prototype website usable for multiple users at once, we decided to limit the number of commits analyzed to the latest $10000$ commits. However, this practical limit may be increased by allowing more worker processes to rate repositories at once, reducing the chance of the entire commit rater being blocked for a long time by large repositories.
